First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-04-21 eg6-letters/coherent/dvcs_he4_prl.tex
Corrections to the PRL coherent

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {R.~Dupr\'{e}} 
\email[corresponding author: ]{dupre@ipno.in2p3.fr}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {K.~Hafidi} 
\affiliation{\ANL}
\author{S.~Stepanyan}
\affiliation{\JLAB}
\author {S.~Bultmann} 
\affiliation{\ODU}
\author{R.~De~Vita} 
\affiliation{\INFNGE}
\author {A.~El~Alaoui} 
\affiliation{\ANL}
\affiliation{\UTFSM}
\author {L.~El~Fassi} 
\affiliation{\MISS}
\author{H.~Egiyan}
\affiliation{\JLAB}
\author{F.X.~Girod} 
\affiliation{\JLAB}
\author{D.~Jenkins}
\affiliation{\VIRGINIATECH}
\author{S.~Liuti} 
\affiliation{\VIRGINIA}
\author{Y.~Perrin}
\affiliation{\ORSAY}
\author {B.~Torayev} 
\affiliation{\ODU}
\author {E.~Voutier} 
\affiliation{\ORSAY}

@@

The $^4$He nucleus is an ideal experimental target for DVCS on nuclei, as it is light enough to be detected in such a setting, while it is subject to significant nuclear effects 
\cite{JSeely} and has rather high density. A helium target leads to another 
important advantage, as the number of GPDs defined for a hadron depends on its 
spin. The structure of a spin-zero nucleus, such as $^4$He, is parametrized by 
only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
arise in the nucleon case. This significantly simplifies the interpretation of 
the data and allows a model independent extraction of the $^4$He CFF 
($\mathcal{H}_{A}$) presented at the end of this letter.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using their measured momentum, time, and energy obtained from 
the CLAS drift chambers, Cerenkov counters, scintillator counters, 
and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
the RTPC using time, track quality, and energy-loss cuts for tracks in the 
fiducial region. In addition, we apply a vertex-matching cut to ensure that the 
electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. This is 
motivated by the fact that, while soft photons are likely to be produced in 
random coincidence, they cannot be mistaken for the large energy DVCS photons 
($>2$ GeV). The most energetic photon is always considered as the DVCS photon 
candidate.

@@

Due to limited statistics, dependence of the extracted asymmetries on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In Fig.~\ref{fig:alu}, $A_{LU}$ for 
bins in each of the three variables is presented. The curves on the plots are fits with 
the function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
Fig.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect on the quark 
distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
different kinematics than our data but still provide some guidance. The 
experimental results appear to have a larger asymmetries than the calculations
in the $x_B = 0.307$ bin. The difference may arise from the theoretical 
uncertainty in the determination of the crossing point between the 
antishadowing region, where the parton nuclear distribution is larger than the 
nucleon one, and the EMC effect region, where the nuclear effect reverses its 
sign.

>>>>

\author {M.~Hattawy}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {N.A.~Baltzell} 
\affiliation{\ANL}
\affiliation{\JLAB}
\author {R.~Dupr\'{e}} 
\email[corresponding author: ]{dupre@ipno.in2p3.fr}
\affiliation{\ANL}
\affiliation{\ORSAY}
\author {K.~Hafidi} 
\affiliation{\ANL}
\author{S.~Stepanyan}
\affiliation{\JLAB}
\author {S.~Bultmann} 
\affiliation{\ODU}
\author{R.~De~Vita} 
\affiliation{\INFNGE}
\author {A.~El~Alaoui} 
\affiliation{\ANL}
\affiliation{\UTFSM}
\author {L.~El~Fassi} 
\affiliation{\MISS}
\author{H.~Egiyan}
\affiliation{\JLAB}
\author{F.X.~Girod} 
\affiliation{\JLAB}
\author {M.~Guidal} 
\affiliation{\ORSAY}
\author{D.~Jenkins}
\affiliation{\VIRGINIATECH}
\author{S.~Liuti} 
\affiliation{\VIRGINIA}
\author{Y.~Perrin}
\affiliation{\ORSAY}
\author {B.~Torayev} 
\affiliation{\ODU}
\author {E.~Voutier} 
\affiliation{\ORSAY}

@@

The $^4$He nucleus is an ideal experimental target for DVCS on nuclei, as it 
is light enough to be detected in such a setting, while it is subject to 
significant nuclear effects~\cite{JSeely} and has a spin-0. A helium target leads to another 
important advantage, as the number of GPDs defined for a hadron depends on its 
spin. The structure of a spin-zero nucleus, such as $^4$He, is parametrized by 
only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
arise in the nucleon case. This significantly simplifies the interpretation of 
the data and allows a model independent extraction of the $^4$He CFF 
($\mathcal{H}_{A}$) presented at the end of this letter.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using their measured momentum, time, and energy obtained from 
the CLAS drift chambers, Cerenkov counters, scintillator counters, 
and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
the RTPC using time, track quality, and energy-loss cuts for tracks in the 
fiducial region. In addition, we apply a vertex-matching cut to ensure that the 
electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. Indeed,
soft photons are produced at very high rates by the electron beam and create 
numerous accidental coincidences. These do not affect directly our mesurement, 
where only the most energetic photon is considered as DVCS photon candidate.
This prescription however slightly increases the corrections associated with
the $\pi^0$ and the accidental backgrounds discussed below.

@@

Due to limited statistics, dependence of the extracted asymmetries on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In Fig.~\ref{fig:alu}, $A_{LU}$ for 
bins in each of the three variables is presented. The curves on the plots are fits with 
the function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
Fig.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect on the quark 
distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
different kinematics than our data but still provide some guidance. The 
experimental results appear to have a larger asymmetries than the calculations. 
The difference may arise from the theoretical uncertainty in the determination 
of the crossing point where the parton nuclear distribution becomes larger than the 
nucleon one, and reverses the sign of the nuclear effect.
